---
title: "Aufgabe_1"
author: "windijon"
date: '2022-04-22'
output: beamer_presentation
---


Task 1: Import data

```{r message = FALSE}

library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data

Wildschwein_Daten <- read_csv(file = "wildschwein_BE.csv")
View(Wildschwein_Daten)

```


Task 2: Explore Data

```{r message = FALSE, warning=FALSE}

ggplot(Wildschwein_Daten, aes(Long, Lat, colour = TierID)) +
  geom_point()

```


Input I: Handling spatial data (Tabelle in Spatial Object umwandeln)

```{r message = FALSE, warning=FALSE}

library(sf)

wildschwein_BE_sf <- st_as_sf(Wildschwein_Daten,             # Tabelle in Spatial Object umwandeln
                              coords = c("Long", "Lat"), 
                              crs = 4326)

View(Wildschwein_Daten)

wildschwein_BE_sf

is.data.frame(wildschwein_BE_sf) # -> [1] TRUE

# subset rows
wildschwein_BE_sf[1:10,]
wildschwein_BE_sf[wildschwein_BE_sf$TierName == "Sabi",]

# subset colums
wildschwein_BE_sf[,2:3]

wildschwein_BE <- st_as_sf(Wildschwein_Daten, 
                          coords = c("Long", "Lat"), 
                          crs = 4326)

rm(wildschwein_BE_sf) 
# we can remove this sf object, since it just eats up our memory

```


Task 3: Project data from WGS84

```{r message = FALSE}

st_transform(x = wildschwein_BE, crs =  2056)

```


Input II: Calculate Convex Hull (aus Punktwolke Polygone machen)

```{r message = FALSE}

wildschwein_BE_grouped <- group_by(wildschwein_BE,TierID)
wildschwein_BE_grouped

wildschwein_BE_sample <- sample_n(wildschwein_BE_grouped, 2000)

wildschwein_BE_smry <- summarise(wildschwein_BE_sample)
wildschwein_BE_smry

mcp <- st_convex_hull(wildschwein_BE_smry)
mcp

```


Task 4: Ploting spatial objects

```{r message = FALSE, warning=FALSE}

plot(mcp)

ggplot(mcp, aes(colour = TierID)) +
  geom_sf() +
  coord_sf(datum =2056)

```


Input III: Importing raster data (import swisstopo-Map)

```{r message = FALSE, warning=FALSE}

library(terra)
  
pk100_BE <- terra::rast("pk100_BE.tif")
pk100_BE

plot(pk100_BE)

plotRGB(pk100_BE)

```


Task 5: Adding a background map (Karte und Wildschwein-Daten zusammen plotten)

```{r message = FALSE, warning=FALSE}

library(tmap)

tmap_mode("plot")

map1 <- tm_shape(shp = pk100_BE) + 
  tm_rgb() +
  tm_shape(shp = mcp) +
  tm_polygons("TierID", border.col = "black", lwd = 1.5, alpha = 0.4) +   # alpha = transparency
  tm_layout(legend.title.size = 1,
            legend.text.size = 0.6,
            legend.position = c("left","top"),
            legend.bg.color = "white",
            legend.bg.alpha = 1,
            frame = F)
  
map1

```


Task 6: Create an interactive map

```{r message = FALSE, warning=FALSE}

map1 <- tm_shape(shp = pk100_BE) + 
  tm_rgb() +
  tm_shape(shp = mcp) +
  tm_polygons("TierID", border.col = "black", lwd = 1.5, alpha = 0.4) +   # alpha = transparency
  tm_compass(type = "arrow", position = c(0.23,0.021), bg.color = "white", bg.alpha = 0.75, size = 1.8) + 
  tm_scale_bar(breaks = c(0, 0.5, 1, 1.5, 2), text.size = 0.75, position = c("left", "bottom"), bg.color = "white", bg.alpha = 0.75) +
  tm_credits("Scale: 1:25'000 \nData source: swisstopo, ZHAW \nAuthor: Jonas M. Windisch", fontface = "italic",  bg.color = "white", bg.alpha = 0.75, width = 1, position = c(0.73,0.02)) +
  tm_logo(file = "zhaw_lsfm_iunr_schwarz.png", position = c(0.79,0.86)) + 
  tm_layout(main.title = " Movement Patterns of Wild-Boar (Sus Scrofa) in the Seeland District (2014-2015)",
            main.title.size = 1,
            legend.title.size = 1,
            legend.text.size = 0.6,
            legend.position = c("left","top"),
            legend.bg.color = "white",
            legend.bg.alpha = 1,
            frame = F)

map1

tmap_mode("view")
map1  + tm_minimap()

tmap_mode("plot")
tmap_save(tm = map1, filename = "Aufgabe1.pdf", width = 17, height = 14, units = "cm", dpi = 5000)

```

